---
title: "BoE_Technical Assessmnet"
author: "Federica Mascolo"
date: "2/26/2022"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(magrittr)
library(ggplot2)
library(readr)
library(openxlsx)
library(dplyr)
library(tidyr)

library(skimr)
library(DataExplorer)
library(glmnet)
library(caTools)
library(ROCR)

```


```{r, echo =FALSE}
setwd("C:/Users/feder/Desktop/Applications/Applications varie/21-22/BoE_technical assessment")
df <- read.xlsx("Data for technical assessment.xlsx")
```


```{r, echo = FALSE}
# clean currency symbol and rename
names(df) <- gsub("\\(£m)", "", names(df))
names(df) <- gsub("\\.", "_", names(df))

#rename(df, 'equity' = "Excess_of_assets_over_liabilities__[=_equity]")

#define a list of varying "varname"
varname <- c('NWP', 'SCR', 'EoF_for_SCR', 'SCR_coverage_ratio' , 'GWP', 'Total_asset' , 'Total_liabilities', 'Excess_of_assets_over_liabilities__[=_equity]')

#define the most recent year in the dataset for each variable
n <- c(20, 20, 20, 20, 20, 20, 20, 20) 

#add the year to the variable name
names(df)[2:ncol(df)] <- unlist(mapply(function(x,y) paste(x, seq(16,y), sep="_"), varname, n))

names(df)[37] <- "equity_16"
names(df)[38] <- "equity_17"
names(df)[39] <- "equity_18"
names(df)[40] <- "equity_19"
names(df)[41] <- "equity_20"
names(df)[1]  <- "firm_id"

df <- subset(df, firm_id != "year")

```

 

```{r, echo = FALSE, results = 'hide'}

# data type 
sapply(df, is.numeric)

# convert all vars to numeric 
cols <- names(df)[2:41]
df[cols] <- lapply(df[cols], as.numeric)

# Basic information on the dataset: no missing, no duplicates 
skim(df)
# automatic report 
DataExplorer:: create_report(
	df,
	config = list(
		"introduce" = list(),
		"plot_str" = list(
			"type" = "diagonal",
			"fontSize" = 35,
			"width" = 1000,
			"margin" = list("left" = 350, "right" = 250)
		),
	
	"plot_missing" = list(),
  "plot_histogram" = list(),
  "plot_density" = list(),
  "plot_qq" = list(sampled_rows = 1000L),
  "plot_correlation" = list("cor_args" = list("use" = "pairwise.complete.obs")),
  "plot_prcomp" = list(),
  "plot_boxplot" = list(),
  "plot_scatterplot" = list(sampled_rows = 1000L)

 
	)
)

# Further look at the correlation matrix
#library("Hmisc")
#df_c <- df[2:41]
#corr_matrix <- rcorr(as.matrix(df_c))
#corr_matrix



```

# Task I: Important firms 

GWP and Total assets have been used as proxies for the firm size. Bigger firms are more important. The histograms below show respectively the first 40 firms with the highest values of GWP and Total assets for 2020. The scatterplot show the two measures jointly. On the x-axes the GWP in 2020. 


```{r, echo = FALSE, warning= FALSE}

# Variables inspected for firm size: GWP and total assets 

# GWP: plot the first 40 frims (bit more then 10% of the sample) wiht the highest GWP in 2020 
firm_size <- df[c(1, 26)]
firm_size <- as.data.frame(firm_size)

firm_size_2 <-firm_size[order(-firm_size$GWP_20),]
firm_size_top <- firm_size_2[1:40,]

plot_size <- ggplot(firm_size_top, aes(x = reorder(firm_id, GWP_20), y = GWP_20)) + 
  geom_col(width = 0.5, fill="#69b3a2", color="#e9ecef", alpha=0.8) +
  coord_flip() +
  theme(axis.text.y = element_text( size = 8))


plot_size 


# Total assets: proxy for firm size 
firm_size2 <- df[c(1, 31)]
firm_size2 <- as.data.frame(firm_size2)

# trim the lower part of the distribution since we are interested in big firms 
lower_quantile <- quantile(firm_size2$Total_asset_20, 0.1, na.rm = TRUE)

# col a where a > its 90th percentile becomes NA
firm_size2$Total_asset_20[firm_size2$Total_asset_20 < lower_quantile] <- NA

# Plot the first 40 firms with highest total assets
firm_size_2 <-firm_size2[order(-firm_size2$Total_asset_20),]
firm_size_top2 <- firm_size_2[1:40,]

plot_size <- ggplot(firm_size_top2, aes(x = reorder(firm_id, Total_asset_20), y = Total_asset_20)) + 
  geom_col(width = 0.5, fill="#69b3a2", color="#e9ecef", alpha=0.8) +
  coord_flip() +
  theme(axis.text.y = element_text( size = 8))

plot_size 


# Scatterplot of the two variables 

#Leave out zeros from the joint sample 
firm_size_joint <- df[c(1, 26, 31)]
firm_size_joint <- subset(firm_size_joint, firm_size_joint$Total_asset != 0 & firm_size_joint$GWP != 0)


scatter_size <- ggplot(firm_size_joint, aes(x = GWP_20, 
               y = Total_asset_20
               )) + 
  geom_point(color = "cornflowerblue",
             alpha = .6,
             size = 5)

scatter_size 


# Let's plot the biggest firms with labels 
scatter_size <- ggplot(firm_size_joint, aes(x = GWP_20, 
               y = Total_asset_20
               )) + 
  geom_point(color = "cornflowerblue",
             alpha = .6,
             size = 2) +
  xlim(0, 50000.0) + 
  ylim(50000.0, 350000.0) + 
   geom_text(aes(label= firm_id) , size = 2.5)


scatter_size 


```

# Measure of risk: 
The SCR coverage ratio hasa been used as a measure of risk for the firms. Firms with SCR coverage ratio lower than one are not able to meet the capital requirements. Therefore is important to check which firms are in this position. 96% of them report SCR coverage ratio equal to zero and in the histogram are reported only firms with negative or lower than one SCR coverage ratio values. 

```{r, echo = FALSE, warning= FALSE}

#SCR: check if big firms do not have SCR > 1, not have buffer 
scr_ratio <- df[c(1,21)]

# check bounds 
summary(scr_ratio)

# check for outliers
scr_ratio1 <- subset(scr_ratio, SCR_coverage_ratio_20 > 1000 )

# clean outliers
scr_ratio <- subset(scr_ratio, SCR_coverage_ratio_20 < 1000 )

# Plot the distribution: it is already in the general report, firms with negative coverage ratio need attention or below 100% need attention 
scr_ratio  <- scr_ratio[order(scr_ratio$SCR_coverage_ratio_20),]

# check: about 96% of obs have cov_ratio equal to zero, only two firms have negative cov ratio 
scr_ratio_less1  <- subset(scr_ratio, SCR_coverage_ratio_20 < 1 & SCR_coverage_ratio_20 != 0)

plot_ratio <- ggplot(scr_ratio_less1, aes(x = reorder(firm_id,SCR_coverage_ratio_20 ), 
                                    y = SCR_coverage_ratio_20)) + 
  geom_col(width = 0.5, fill="#69b3a2", color="#e9ecef", alpha=0.8) + 
  coord_flip()

# Firm 141 and 109 
plot_ratio

```

# Gross claims incurred:  
The Gross claims incurred is used as a proxy for the risk of the firm. An high change between 2020 and 2019 in the Gross claims incurred can be considered as a big cost for the firm and a criterion to consider when allocating resources. 
```{r , echo = FALSE}
setwd("C:/Users/feder/Desktop/Applications/Applications varie/21-22/BoE_technical assessment")
df_under <- read.xlsx("Data for technical assessment.xlsx", sheet = "Dataset 2 - Underwriting")
```

The histograms below show the first two firms with the biggest percentage change in the gross claims incurred between 2019 and 2020. While the second histogram shows from the third to the 40th firm with the bigger percentage change in the same variable. Finally, the scatterplot shows firms with higher values for total assets and Gross claims incurred. 
```{r , echo = FALSE}

names(df_under) <- gsub("\\(£m)", "", names(df_under))
names(df_under) <- gsub("\\.", "_", names(df_under))

#define a list of varying "varname"
varname <- c('Gross_claims_incurred', 'Gross_BEL_(inc__TPs_as_whole,_pre-TMTP)_', 'Net_BEL_(inc__TPs_as_a_whole,_pre-TMTP)_', 'Pure_net_claims_ratio' , 'Net_expense_ratio', 'Net_combined_ratio' , 'Pure_gross_claims_ratio', 'Gross_expense_ratio', 'Gross_combined_ratio')

#define the most recent year in the dataset for each variable
n <- c(20, 20, 20, 20, 20, 20, 20, 20, 20) 

#add the year to the variable name
names(df_under)[2:ncol(df_under)] <- unlist(mapply(function(x,y) paste(x, seq(16,y), sep="_"), varname, n))


names(df_under)[1]  <- "firm_id"
df_under <- subset(df_under, firm_id  != "")

# convert all vars to numeric 
cols <- names(df_under)[2:46]
df_under[cols] <- lapply(df_under[cols], as.numeric)

```


```{r, echo =FALSE}
# gen percentage change in gross claims incurred: big change may indicate a not stable position for the firm

df_under <- df_under %>%
   mutate(per_change_gci = 
            (
              ifelse( Gross_claims_incurred_20 <0 & Gross_claims_incurred_19 <0, 
                -( ((Gross_claims_incurred_20 - Gross_claims_incurred_19)/Gross_claims_incurred_19)*100),
          ((Gross_claims_incurred_20 - Gross_claims_incurred_19)/Gross_claims_incurred_19)*100)))

df_change_gci <- df_under[c(1,47)]
df_pos_gci <- subset(df_change_gci, (!is.na(df_change_gci$per_change_gci) & df_change_gci$per_change_gci > 0) & df_change_gci$per_change_gci != Inf )

# Select the 40 higest change 
df_pos_gci <- df_pos_gci[order(-df_pos_gci$per_change_gci),]

# after subsetting for the first 40 firms, suggested to leave out the first 2 or three highest to see better the size of the remaining and understand the how the change of the firm at the margin compare to the others. 
df_pos_gci_top_2 <- df_pos_gci[1:2,]

### Important: leaving out the first two highest changes 
df_pos_gci_top <- df_pos_gci[3:40,]


# Positive changes indicates a large cost for an insurer that may needs funds 
plot_changes <- ggplot(df_pos_gci_top_2, aes(x = reorder(firm_id, per_change_gci), 
                                          y = per_change_gci )) + 
  geom_col(width = 0.5, fill="#69b3a2", color="#e9ecef", alpha=0.8) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

plot_changes




# Positive changes indicates a large cost for an insurer that may needs funds 
plot_changes <- ggplot(df_pos_gci_top, aes(x = reorder(firm_id, per_change_gci), 
                                          y = per_change_gci )) + 
  geom_col(width = 0.5, fill="#69b3a2", color="#e9ecef", alpha=0.8) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

plot_changes



# Joint plot firm with biggest change and assets 

#merge the dataset on firms 
#round(firm_size2$Total_asset, digits = 6)
merged <- merge(df_pos_gci_top, firm_size2, by  = "firm_id" )



# Scatterplot of the two variables 
scatter_change_size <- ggplot(merged, aes(x = per_change_gci, 
               y = Total_asset_20
               )) + 
  geom_point(color = "cornflowerblue",
             alpha = .6,
             size = 3) +
  xlim(0, 20000.0) + 
  ylim(0, 350000.0) 

scatter_change_size 


# Scatterplot of the two variables: change size to exclude extreme values 
scatter_change_size <- ggplot(merged, aes(x = per_change_gci, 
               y = Total_asset_20
               )) + 
  geom_point(color = "cornflowerblue",
             alpha = .6,
             size = 3) +
  xlim(0, 3000.0) + 
  ylim(0, 3000.0) + 
   geom_text(aes(label= firm_id) , size = 2.5)

scatter_change_size 

# select only frims with values of both variables higher than the third quartile
summary(merged)
# per_change_gci = 106 
# Tot_asset = 42

# Create a subset for the firms with percentage change in gci and total assets higher than the mean values. 
resources_to_all <- subset(merged, per_change_gci >= 107 & Total_asset_20 >=42)

```


```{r , echo=FALSE}
df_full <- merge(df, df_under, by = "firm_id")

# convert all vars to numeric 
cols <- names(df_full)[2:87]
df_full[cols] <- lapply(df_full[cols], as.numeric)

```

# Selection of firms: 
The dataset below shows the biggest firms in terms of total assets and highest claims. The two variables are considered the most important measures to consider when allocating resources to a firm. 
To validate the analysis the dataset shows the percentage deviation from the mean values and the variance by firm of both variables. 
```{r, echo = FALSE }

# merge with full dataset to check the two variabels over time 
resources_to_all_ts <- merge(resources_to_all, df_full, by = "firm_id" )

resources_to_all_ts <- resources_to_all_ts[c(1:3, 29:32, 44:48 )]
names(resources_to_all_ts)[3] <- "Total_asset_20"
names(resources_to_all_ts)[2] <- "per_change_gci"


# I expect total assets to not devatiate from the mean value (otherwise there can be reporting error, while for the detected firms I would expect the change in claims to devate from the mean value)

resources_to_all_ts <- resources_to_all_ts %>%
  mutate(mean_tot_asset = (Total_asset_16 + Total_asset_17 + Total_asset_18 + Total_asset_19)/ 4,
         mean_gci = (Gross_claims_incurred_16 + Gross_claims_incurred_17 + Gross_claims_incurred_18 + Gross_claims_incurred_19)/4, 
         per_dev_tot_asset = ((Total_asset_20 - mean_tot_asset)/ mean_tot_asset) *100, 
         per_dev_gci = ((Gross_claims_incurred_20 - mean_gci)/ mean_gci)*100 , 

         )


resources_to_all_ts <- resources_to_all_ts %>%
  mutate(mean_tot_asset = (Total_asset_16 + Total_asset_17 + Total_asset_18 + Total_asset_19 + Total_asset_20)/ 5,
         mean_gci = (Gross_claims_incurred_16 + Gross_claims_incurred_17 + Gross_claims_incurred_18 + Gross_claims_incurred_19 + Gross_claims_incurred_20 )/5, 
         var_gci = (
           (Gross_claims_incurred_16  - mean_gci)^2 + (Gross_claims_incurred_17 - mean_gci)^2 + (Gross_claims_incurred_18 - mean_gci)^2 + (Gross_claims_incurred_19 - mean_gci)^2 + (Gross_claims_incurred_20 - mean_gci )^2 )/4 ,
        var_tot_asset = (
         ( Total_asset_16 - mean_tot_asset)^2 +  ( Total_asset_17 - mean_tot_asset)^2 +  ( Total_asset_18 - mean_tot_asset)^2 +  ( Total_asset_19 - mean_tot_asset)^2 +  ( Total_asset_20 - mean_tot_asset)^2 )/4
         )


round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

# Inspect the data 
resources_to_all_ts <- round_df(resources_to_all_ts, 4)

resources_to_all_ts <- resources_to_all_ts[c(1:3, 15:18)]

#kable(head(resources_to_all_ts, n=8), format = "markdown")

head(resources_to_all_ts, n=8)
```


# Task II: ML classifification of healthy/unhealthy firms 
The supervised ML algorithm below is a LASSO regularization used to classify healthy and unhealthy firms.  The dependent variable is the equity of the firm in 2020 modeled as a binary variable: firms with equity greater than zero are considered healthy while the rest are classified as unhealthy. The lambda parameter for LASSO has been selected with cross-validation. The assessment methods are the test error, calculated as the one minus the accuracy, and the False Positive Rate. Indeed, our focus is to reduce the number of firms wrongly classified as healthy. 
```{r, echo = FALSE, warning = FALSE }

# y variable: equity in 2020 
summary(df_full$equity_20)


# y varibale 
df_full <- df_full  %>%
   mutate( h_firm = ifelse(equity_20 > 0, 1 ,0))   
summary(df_full$h_firm)

df_full <- df_full[c(2:26, 37:40, 42:86, 88)]


set.seed(2)

split = sample.split(df_full$h_firm, SplitRatio = 6/10)
train = subset(df_full, split == TRUE)
test= subset(df_full, split == FALSE)


x.train = model.matrix(h_firm ~ . , data = train)
y.train = (train$h_firm)

x.test = model.matrix(h_firm ~ ., data =test)
y.test = (test$h_firm)

fit.lasso = glmnet(x.train, y.train, alpha = 1, family = "binomial")


#CV lasso 
cv.lasso = cv.glmnet(x.train, y.train, alpha = 1, family = "binomial", parallel = TRUE)
par(mfrow = c(1,2))
plot(fit.lasso, xvar = "lambda", label = TRUE)
plot(cv.lasso)
coef(cv.lasso)

pred.lasso = predict(cv.lasso, x.test, s = cv.lasso$lambda.1se, type = "response")


#ROC curve 
predob = prediction(pred.lasso, y.test)
perf = performance(predob, "tpr", "fpr")
par(mfrow = c(1,1))
plot(perf, main = "Lasso test ROC", colorize = TRUE)
as.numeric(performance(predob, "auc")@y.values)


#refit the model with the defined threshold 
lasso.pred = ifelse(pred.lasso > 0.5, 1, 0)

table = table(test$h_firm, lasso.pred)
#table

lasso.testerror = 1-sum(diag(table))/sum(table)
FPR = table[1,2]/(table[1,2] + table[2,2])


data.table(lasso.testerror, FPR)

```


